---
title: "Calculating Expected Offspring"
author: "Dominic Pearce"
date: "16 February 2016"
output:
  prettydoc::html_pretty:
    highlight: github
    theme: cayman
---

```{r, include = FALSE, cache = TRUE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```


&nbsp;

Given a parent-couple population defined by the order:

1. AA-AA
2. AA-Aa
3. AA-aa
4. Aa-Aa
5. Aa-aa
6. aa-aa

Return the expected number of dominant offspring, given 2 children per parent-couple

&nbsp;

### Libraries
```{r}
library(knitr) #for prettier markdown tables
```

&nbsp;

## First create a `data.frame()` with the probabilities of each parent-couple having a dominant child

```{r}
probfreq.tbl <- data.frame(p.genotype = c("AA-AA", "AA-Aa", "AA-aa", "Aa-Aa", "Aa-aa", "aa-aa"), prob.dom = c(1, 1, 1, 0.75, 0.5, 0))

kable(probfreq.tbl)
```

&nbsp;

## Then add our parent-couple frequencies
### and multiply by two to get the number of children

```{r}
probfreq.tbl$pop.freq <-  as.numeric(strsplit(readLines("~/Downloads/rosalind_iev.txt"), " ")[[1]])

probfreq.tbl$children <- probfreq.tbl$pop.freq*2

kable(probfreq.tbl)
```

&nbsp;

## Multiply offspring frequencies by likelyhood of dominant offspring and `Sum()`

```{r}
probfreq.tbl$children.dom <- probfreq.tbl$prob.dom * probfreq.tbl$children

kable(probfreq.tbl)

sum(probfreq.tbl$children.dom)
```

&nbsp;

## Clean code
```{r, eval=FALSE}
probfreq.tbl <- data.frame(p.genotype = c("AA-AA", "AA-Aa", "AA-aa", "Aa-Aa", "Aa-aa", "aa-aa"),
                           prob.dom = c(1, 1, 1, 0.75, 0.5, 0),
                           pop.freq =  as.numeric(strsplit(readLines("~/Downloads/rosalind_iev.txt"), " ")[[1]]))

probfreq.tbl$children <- probfreq.tbl$pop.freq*2

sum(probfreq.tbl$prob.dom * probfreq.tbl$children)
```
