---
title: "Finding a Spliced Motif"
author: "Dominic Pearce"
date: "14 April 2016"
output: github_document
---

# {.tabset}

## Method 1
### Define sequence (`seq`) and subsequence (`subseq`)
#### `subseq` is split into individual nucleotides to be worked on one at a time in a loop

```{r}
seq <- "ACGTACGTGACG"

subseq <- c("G", "T", "A")
```

&nbsp;

### Loop over `subseq` to retrieve a vector of each nucleotides location**s** in seq
```{r}
nuc.positions <- lapply(subseq, function(x) as.numeric(unlist(gregexpr(x, seq))))

nuc.positions
```

&nbsp;

### Then we create a function that
#### - randomly samples each nucleotide's positions, one at a time and once for each nucleotide in subseq
#### - asks whether this random sampling is identical to its own ascending order-sorted brother
#### - if `TRUE` then great, that's our answer
#### - if `FALSE` then we repeat the procedure by calling the function `findPositions()` again, from within itself
#### - this will then repeat until a `TRUE` is achieved

```{r}
findPositions <- function(x) {

  tmp.samp <- unlist(lapply(x, function(y) sample(y, 1)))

  if (identical(sort(tmp.samp), tmp.samp) == TRUE) {
    tmp.samp
  } else { findPositions(x)
  }
}
```

### The answer
```{r}
findPositions(nuc.positions)
```

&nbsp;

### **BUT!** Disaster! This only works for the model data

```{r, echo=FALSE, error = TRUE}
options(expressions = 500000)

input <- readLines("C:/Users/domin/Downloads/rosalind_sseq (3).txt")

seq <- paste0(input[2:16], collapse = "")
subseq <- strsplit(paste(input[18:19], collapse = ""), split = "")[[1]]

nuc.positions <- lapply(subseq, function(x) as.numeric(unlist(gregexpr(x, seq))))

findPositions(nuc.positions)
```

### The real data is too much for the computer to handle in this manner
#### (nice [**stack overflow**](http://stackoverflow.com) error message however)

## Method 2

### Same as before, up until the part where we need to get the ordered indicies

```{r}
input <- readLines("~/Downloads/rosalind_sseq.txt")

seq <- paste0(input[2:16], collapse = "")
subseq <- strsplit(paste(input[18:19], collapse = ""), split = "")[[1]]

nuc.positions <- lapply(subseq, function(x) as.numeric(unlist(gregexpr(x, seq))))
```

&nbsp;

#### This time we use a for loop where, for each of the indicies we simply grab the **smallest available that is higher than the previous index in the sequence**

#### This requires us to:
#### - first set a variable `index` with a 0 value otherwise the whole thing falls apart
#### - subset by values that are higher than zero (for the first iteration), and higher than the previous answer for the subsequent loops
#### - take the smallest index of that subset

```{r}
index <- c(0)

for (i in 1:length(nuc.positions)) {

  sub.positions <- nuc.positions[[i]][which(nuc.positions[[i]] > index[length(index)])]

  index <- c(index, head(sub.positions, n = 1))
}


cat(index[-1])
```
