---
title: "Rosalind Problems"
author: "Dominic Pearce"
date: "16 October 2015"
output: slidy_presentation
---

##Counting DNA Nucleotides

##Counting DNA Nucleotides
Load
```{r}
#Load problem file
ess <- colnames(read.delim("C:/Users/s1460988/Downloads/rosalind_dna (3).txt"))
head(ess)
```

##Counting DNA Nucleotides
Split to individual nucleotides using `strsplit()` setting argument `split = ""`
```{r}
split.ess <- strsplit(ess, split = "")

head(split.ess[[1]])
```

##Counting DNA Nucleotides
Count occurences using `table()`
```{r}
table(split.ess)
```


##Transcribing DNA into RNA

##Transcribing DNA into RNA
Again load and split
```{r}
asdf <- colnames(read.delim("C:/Users/s1460988/Downloads/rosalind_rna (2).txt"))
head(asdf)
```

##Transcribing DNA into RNA
Again load and split
```{r}
fdsa <- strsplit(asdf, "")
head(fdsa[[1]])
```

##Transcribing DNA into RNA
Use `gsub()` to convert T's to U's
```{r}
qwer <- gsub("T", "U", fdsa[[1]])
head(qwer)
```

Use `paste()` to join into one string again, for easy export
```{r}
paste(qwer, collapse = "")
```


```{r}
##Reverse Transcription

asdf <- colnames(read.delim("C:/Users/s1460988/Downloads/rosalind_revc (4).txt"))

fdsa <- strsplit(asdf, "")

tmp1 <- gsub("A", "1", fdsa[[1]])
tmp2 <- gsub("C", "2", tmp1)
tmp3 <- gsub("T", "A", tmp2)
tmp4 <- gsub("G", "C", tmp3)
tmp5 <- gsub("1", "T", tmp4)
tmp6 <- gsub("2", "G", tmp5)

paste(rev(tmp6), collapse = "")
```

```{r, eval=FALSE, include=FALSE}
## Counting Point Mutations
data <- as.matrix(read.delim("C:/Users/s1460988/Downloads/rosalind_hamm(1).txt", header = FALSE))

data.tmp <- lapply(data, function(x) strsplit(x, ""))

data.split <- as.data.frame(data.tmp, stringsAsFactors = FALSE)

point.muts <- apply(data.split, 1, function(x) identical(x[[1]], x[[2]]))

table(point.muts)
```

