---
title: "DNA-complementation"
author: "Dominic Pearce"
date: "25 January 2016"
output: slidy_presentation
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, fig.align='center')
```

## Complementing DNA
Read in data using `readLines()`
```{r}
input.raw <- readLines("//cmvm.datastore.ed.ac.uk/igmm/sims-lab/Dominic/_PhD/Projects/Labbook/zMisc/Rosalind/Complementing a Strand of DNA/rosalind_revc.txt")

substr(input.raw, 1, 6)
```

## Complementing DNA
Read in data using `readLines()` and split to individual nucleotides with `strsplit()`
```{r}
input.raw <- readLines("//cmvm.datastore.ed.ac.uk/igmm/sims-lab/Dominic/_PhD/Projects/Labbook/zMisc/Rosalind/Complementing a Strand of DNA/rosalind_revc.txt")

substr(input.raw, 1, 6)

input <- strsplit(input.raw, "")[[1]]

head(input)
```

## Complementing DNA
Form complement strand using a series of character replacements with `gsub()`
```{r}
tmp1 <- gsub("A", "1", input)

head(input)
```

## Complementing DNA
Form complement strand using a series of character replacements with `gsub()`
```{r}
tmp1 <- gsub("A", "1", input)

head(input)
head(tmp1)
```

## Complementing DNA
Form complement strand using a series of character replacements with `gsub()`
```{r}
tmp1 <- gsub("A", "1", input)
tmp2 <- gsub("C", "2", tmp1)

head(tmp1)
```

## Complementing DNA
Form complement strand using a series of character replacements with `gsub()`
```{r}
tmp1 <- gsub("A", "1", input)
tmp2 <- gsub("C", "2", tmp1)

head(tmp1)
head(tmp2)
```

## Complementing DNA
Form complement strand using a series of character replacements with `gsub()`
```{r}
tmp1 <- gsub("A", "1", input)
tmp2 <- gsub("C", "2", tmp1)
tmp3 <- gsub("T", "A", tmp2)

head(tmp2)
```

## Complementing DNA
Form complement strand using a series of character replacements with `gsub()`
```{r}
tmp1 <- gsub("A", "1", input)
tmp2 <- gsub("C", "2", tmp1)
tmp3 <- gsub("T", "A", tmp2)

head(tmp2)
head(tmp3)
```

## Complementing DNA
Form complement strand using a series of character replacements with `gsub()`
```{r}
tmp1 <- gsub("A", "1", input)
tmp2 <- gsub("C", "2", tmp1)
tmp3 <- gsub("T", "A", tmp2)
tmp4 <- gsub("G", "C", tmp3)

head(tmp3)
```

## Complementing DNA
Form complement strand using a series of character replacements with `gsub()`
```{r}
tmp1 <- gsub("A", "1", input)
tmp2 <- gsub("C", "2", tmp1)
tmp3 <- gsub("T", "A", tmp2)
tmp4 <- gsub("G", "C", tmp3)

head(tmp3)
head(tmp4)
```

## Complementing DNA
Form complement strand using a series of character replacements with `gsub()`
```{r}
tmp1 <- gsub("A", "1", input)
tmp2 <- gsub("C", "2", tmp1)
tmp3 <- gsub("T", "A", tmp2)
tmp4 <- gsub("G", "C", tmp3)
tmp5 <- gsub("1", "T", tmp4)

head(tmp4)
```
## Complementing DNA
Form complement strand using a series of character replacements with `gsub()`
```{r}
tmp1 <- gsub("A", "1", input)
tmp2 <- gsub("C", "2", tmp1)
tmp3 <- gsub("T", "A", tmp2)
tmp4 <- gsub("G", "C", tmp3)
tmp5 <- gsub("1", "T", tmp4)

head(tmp4)
head(tmp5)
```

## Complementing DNA
Form complement strand using a series of character replacements with `gsub()`
```{r}
tmp1 <- gsub("A", "1", input)
tmp2 <- gsub("C", "2", tmp1)
tmp3 <- gsub("T", "A", tmp2)
tmp4 <- gsub("G", "C", tmp3)
tmp5 <- gsub("1", "T", tmp4)
complement <- gsub("2", "G", tmp5)

head(tmp5)
```

## Complementing DNA
Form complement strand using a series of character replacements with `gsub()`
```{r}
tmp1 <- gsub("A", "1", input)
tmp2 <- gsub("C", "2", tmp1)
tmp3 <- gsub("T", "A", tmp2)
tmp4 <- gsub("G", "C", tmp3)
tmp5 <- gsub("1", "T", tmp4)
complement <- gsub("2", "G", tmp5)

head(tmp5)
head(complement)
```

## Complementing DNA
This can also be achieved in one line by building the function recursively
```{r}
complement <- gsub("2", "G", gsub("1", "T", gsub("G", "C", gsub("T", "A", gsub("C", "2", gsub("A", "1", input))))))
```

## Complementing DNA
Reverse the nucleotides using `rev()` and group together as one string with `paste()` for easy export back to Rosalind
```{r}
DNA.out <- paste(rev(complement), collapse = "")
```

## Complementing DNA
Reverse the nucleotides using `rev()` and group together as one string with `paste()` for easy export back to Rosalind 
```{r}
DNA.out <- paste(rev(complement), collapse = "")

substring(input.raw, 1, 6)
```

taking us from this

## Complementing DNA
Reverse the nucleotides using `rev()` and group together as one string with `paste()` for easy export back to Rosalind 
```{r}
DNA.out <- paste(rev(complement), collapse = "")

substring(input.raw, 1, 6)

substring(DNA.out, 1, 6)
```

to this.