---
title: "Inferring mRNA from Protein"
author: "Dominic Pearce"
date: "18 April 2016"
output: 
  html_document: 
    highlight: kate
    theme: spacelab
---

# Load/Arrange data
```{r}
input <- readLines("C:/Users/domin/Downloads/rosalind_mrna (3).txt")

modu <- 1000000
```

&nbsp;

# Create redundency data frame
#### The input is taken from the conversion table and allows us to count how many ways there are to achieve each protein
```{r}
conversion.frame <- data.frame(AA = c("F", "L", "I", "V", "F", "L", "I", "V", "L", "L", "I", "V", "L", "L", "M", "V", "S", "P", "T", "A", "S", "P", "T", "A", "S", "P", "T", "A", "S", "P", "T", "A", "Y", "H", "N", "D", "Y", "H", "N", "D", "Stop", "Q", "K", "E", "Stop", "Q", "K", "E", "C", "R", "S", "G", "C", "R", "S", "G", "Stop", "R", "R", "G", "W", "R", "R", "G"), stringsAsFactors = FALSE)
  
redundencies <- data.frame(table(conversion.frame$AA))
redun.dfr <- data.frame(redundencies)

knitr::kable(redun.dfr)
```

&nbsp;

# For each amino acid in our input, return how many possible codons could have coded it 
```{r}
protein <- c(strsplit(input, "")[[1]], "Stop")

protein[1:10]

unproducts <- unlist(lapply(protein, function(x) redun.dfr$Freq[which(redun.dfr$Var1 == x)]))

unproducts [1:10]
```

&nbsp;

# Use a complicated little for loop which I got to work mostly by accident
#### The answer is the product of `unproducts` modulo a million, **BUT** that answer is too large for the computer so...
```{r}
output <- 1
for (i in unproducts) {
  output <- output %% modu * (i %% modu)
}

output %% modu
```

&nbsp;

#### In short ->   

`prod(c(1, 2, 3, 4)) %% 1000000`  

is the same as  

`(((1 * 2) %% 1000000) * 3 %% 1000000) * 4 %% 1000000`

&nbsp;

#### This allows us to build out answer up piece by piece and not cause it to throw a wobbly. By calling `%%` on each step of the answer, it is never able to get larger than 1 million.