---
title: Counting Subsets
output:
  github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.align = 'center')
```

```{r, include = FALSE}
library(tidyverse)
```

#### We want to count the total possible number of subsets of the set *{1,2,…,n}*. This can be represented using Pascal's Triangle. The key concept is that the empty set { } is counted in addition.

&nbsp;

**{ }:** &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; 1 &nbsp; &nbsp; &nbsp; &nbsp; &nbsp;

**{1}:** &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; 1 &nbsp; 1 &nbsp; &nbsp; &nbsp; &nbsp;

**{1, 2}:** &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; 1 &nbsp; 2 &nbsp; 1 &nbsp; &nbsp; &nbsp;

**{1, 2, 3}:** &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; 1 &nbsp; 3 &nbsp; 3 &nbsp; 1 &nbsp; &nbsp;

**{1, 2, 3, 4}:** &nbsp; &nbsp; &nbsp; &nbsp; 1 &nbsp; 4 &nbsp; 6 &nbsp; 4 &nbsp; 1 &nbsp;

&nbsp;

#### But more simply is `2^n`. So, all we need are two variables, `n` to define our set (as 1 to n) and our modulo value which the answer format requires.

&nbsp;

```{r}
n <- 982
modu <- 1000000
```

&nbsp;

#### `2^982` (`4.087481 x 10^295`) is too large for R to comprehend acurately so we have to incrementally calculate our answer, using the principle that `2^3 %% 1000000` is exactly the same as `(2*2 %% 1000000)*2 %% 1000000`.

&nbsp;

```{r}
output <- 1
for (i in rep(2, n)) {
  int <- output %% modu * (i %% modu)
  output <- int %% modu
}
output
```

```{r, include = FALSE}
n = 3
seq <- 1:n

lapply(2:n, function(x) {
    replicate(10, sort(sample(seq, x))) %>%
        data.frame() %>%
        lapply(., list) %>%
        unique()
    }
) %>% unlist(recursive = FALSE) %>% length() %>% sum(., n, 1)
```
