---
title: "Speeding Up Motif Finding"
author: "Dominic Pearce"
date: "28 June 2016"
output: html_document
---

```{r, echo=FALSE}
library(purrr)
```

# {.tabset}

## Our function to solve the problem
```{r}
rosFunc <- function(s, k){  #difficult to name functions when you only slightly understand what they do
  i <- c()
  ii <- c()
  
  for (j in 2:k){
    i[(j-1)] <- substring(s, j, k)
  }
  
  for(j in 2:k){
    ii[j-1] <- substring(s, 1, (k-j+1))
  }
  
  hit <- intersect(i, ii)
  
  ifelse(length(hit) < 1, 0, max(nchar(hit)))
  
}
```

## What is this actually doing? (Using example data)

#### First for a given `k` calculate `s[j:k]` for all `j`s, where `1 < j < k`
```{r}
s <- "CAGCATGGTATCACAGCAGAG"
n <- nchar(s)
k <- 17

i <- c()
for (j in 2:k){
  i[(j-1)] <- substring(s, j, k)
}

i
```

#### Then, again for all possible `j`s, calculate `s[1:k-j+1]`
```{r}
ii <- c()
for(j in 2:k){
  ii[j-1] <- substring(s, 1, (k-j+1))
}

ii
```

#### Now we just need to find the longest common string between these two sets of strings
```{r}
hit <- intersect(i, ii)

hit

max(nchar(hit))
```

And finally, as we'll be dealing with `P[k] = 0` often, which effectively return 'empty' then we fiddle with the output a little but it's not important.
```{r}
ifelse(length(hit) < 1, 0, max(nchar(hit)))
```

## With example data
```{r}
map_dbl(1:n, function(x) rosFunc(s, x))
```

## Is time to completetion linear?
```{r, warning=FALSE, cache=TRUE}
start <- Sys.time()

times <- c()

for (i in 1:400){
  s.rand <- sample(c("A", "C", "G", "T"), i, replace = TRUE) %>% paste0(collapse = "")
  n.rand <- nchar(s.rand)
  
  times[i] <- system.time(map_dbl(1:n.rand, function(x) rosFunc(s.rand, x)))
}

Sys.time() - start

plot(times)
```

