---
title: "Counting Point Mutations"
author: "Dominic Pearce"
date: "5 January 2016"
output: slidy_presentation
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, fig.align='center')
```

## Plan

- Split long character strings into individual nucleotides
- Organise these into individual dataframe cells
- call ```identical()``` 
- count how many instances are ```FALSE```

## Split long character strings into individual nucleotides

```{r}
data <- as.matrix(read.delim("C:/Users/s1460988/Downloads/rosalind_hamm(1).txt", header = FALSE))

data.tmp <- lapply(data, function(x) strsplit(x, ""))
```

## Split long character strings into individual nucleotides

```{r}
data[1]
```

## Split long character strings into individual nucleotides

```{r}
data.tmp[[1]]
```

## Organise these into individual dataframe cells

```{r}
data.split <- as.data.frame(data.tmp, stringsAsFactors = FALSE)
```

```{r, echo=FALSE}
colnames(data.split) <- c("A", "B")
```

## Organise these into individual dataframe cells

```{r}
head(data.split)
```


## call ```identical()``` on each row individually and assign to a new column

```{r}
data.split$match <- apply(data.split, 1, function(x) identical(x[[1]], x[[2]]))
```

## call ```identical()``` on each row individually and assign to a new column

```{r}
head(data.split)
```

## count how many instances are ```FALSE```

```{r}
table(data.split$match)
```

