---
title: Perfect Matchings and RNA Secondary Structures
author: Dominic Pearce
output:
  github_document
---

```{r}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
```

```{r}
rna <- "AGCUAGUCAU" %>% strsplit("") %>% .[[1]]

mtx <- matrix(rep(0, length(rna)^2), ncol = length(rna))
row.names(mtx) <- rna
colnames(mtx) <- rna

sapply(rna, function(x) sapply(mtx, function(y) )

```


2 = 1+1 = 1 + 3^0
5 = 2+3 = 2+ 3^1
14= 5+9 = 5 + 3^2
41 = 14 + 27 = 14 + 3^3

rosCat <- function(len) {
    m <- 1
    n <- 0
    mod <- 1
    while(len-1 > n) {
        m <- m + 3^n
        n <- n + 1
        mod <- mod %% 1000000 * m %% 1000000
    }
    mod
}

s <- "UGAACAUUAGAUUAUCGUAUAGCUAUAAAUUUCUUAGUAUCGAUAUACUUAUAACGAUAAUAUUAGCGCGCAUAUAAUCUACGGUGCAUGCACACUAAUUAAAUGCGAUAUCUGGUACCGAGCGCUUCCGCGCAAUUUGUAUAUAUACAGCGCGCGGAUAUACGUGCCGAUCUUCCGGAUAAGCGUACCGAUGGCGCGCAUAUGCAUAUCAUGGCCACGUGAAUAUUGCUAGAUAUUACG"
nchar(s)

rosCat(1) %% 1000000

rosCat(2) %% 1000000



n <- 3
factorial(2*n) / factorial((n+1)) * factorial(n)
