---
title: "Counting GC Content"
author: "Dominic Pearce"
date: "25 January 2016"
output: slidy_presentation
---

## Counting GC Content
Perform extremely annoying process of getting the data in a managable form
```{r}
input.raw <- readLines("//cmvm.datastore.ed.ac.uk/igmm/sims-lab/Dominic/_PhD/Projects/Labbook/zMisc/Rosalind/GC Content/rosalind_gc.txt")
```

## Counting GC Content
Perform extremely annoying process of getting the data in a managable form
```{r}
input.raw[1:4]
```

## Counting GC Content
Perform extremely annoying process of getting the data in a managable form
```{r}
input.raw[1:4]

length(input.raw)
```

## Counting GC Content
Perform extremely annoying process of getting the data in a managable form
```{r}
input.raw[1:4]

length(input.raw)

nchar(input.raw[2])
```

## Counting GC Content
`Paste()` together as one long string and then split by the FASTA deliminator '>Rosalind_xxxx', leaving only the nucleotide information
```{r}
input.int <- as.data.frame(strsplit(paste(input.raw, collapse = ""), ">Rosalind_...."))

substr(input.int[[1]][2:5], 1, 6)
```

Note: this removes the ">Rosalind_xxxx" information anonymising the different nucleotide strings. This is something must be overcome later on.

## Counting GC Content
`Paste()` together as one long string and then split by the FASTA deliminator '>Rosalind_xxxx', leaving only the nucleotide information
```{r}
input.int <- as.data.frame(strsplit(paste(input.raw, collapse = ""), ">Rosalind_...."))

substr(input.int[[1]][2:5], 1, 6)
```

Split into individual nucleotides and remove list nesting (making sure to set `recursive = FALSE`)

```{r}
input.int2 <- apply(input.int, 1, function(x) strsplit(x, ""))

input.int2[[2]][[1]][1:6]

input <- unlist(input.int2, recursive = FALSE)[2:length(input.int2)]
```

## *Finally* our input for the actual question
```{r}
lapply(input, function(x) head(x[1:6]))
```

## Counting GC Content
Count nucleotide distributions for each case
```{r}
nucleotides <- data.frame(sapply(1:length(input), function(x) table(input[x])))

nucleotides
```

## Counting GC Content
Count nucleotide distributions for each case
```{r}
nucleotides <- data.frame(sapply(1:length(input), function(x) table(input[x])))

nucleotides
```

Calcualte GC content as a percentage
```{r}
GC.content <- sapply(nucleotides, function(x) (x[2] + x[3])/sum(x)*100)
```

## Counting GC Content
GC percentage
```{r}
GC.content
```

## Counting GC Content
GC percentage
```{r}
GC.content
```

Determine the highest percentage
```{r}
max(GC.content)
```

## Counting GC Content
GC percentage
```{r}
GC.content
```

Determine the highest percentage
```{r}
max(GC.content)
```

Which percentage that is
```{r}
which.max(GC.content)
```

## Counting GC Content
GC percentage
```{r}
GC.content
```

Determine the highest percentage
```{r}
max(GC.content)
```

Which percentage that is
```{r}
which.max(GC.content)
```

And finally which instance of the lines containing the character ">" this in turn corresponds to in our original `input.raw`.

```{r}
grep(">", input.raw)

grep(">", input.raw)[which.max(GC.content)]
```

## Subsetting by this index gives us our FASTA ID

```{r}
input.raw[grep(">", input.raw)[which.max(GC.content)]]
```
