---
title: "Independent Alleles"
author: "Dominic A. Pearce"
date: "6 April 2016"
output: github_document
---

```{r, include = FALSE, cache = TRUE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r, echo = FALSE}
library(knitr)
```


# {.tabset}

## First, our input

```{r}
k <- 4
N <- 7
```

## Generation 1

### Simulate our first generation

#### Using 1, 2, 10 & 20 allow us to decipher the genotype simply by summing
```{r}
g1 <- data.frame(replicate(2, c(c(sample(c(20, 10), 1),
                                  sample(c(20, 10), 1)),
                                c(sample(c(2, 1), 1),
                                  sample(c(2, 1), 1)))))

kable(g1)

sapply(g1, sum)
```

## Generation 2

### Simulate our second generation
```{r}
g2 <- sapply(g1, function(x) data.frame(replicate(2,
                                                  c(c(sample(x[1:2], 1),
                                                      sample(c(20, 10), 1)),
                                                    c(sample(x[3:4], 1),
                                                      sample(c(2, 1), 1))))))

g2

kable(data.frame(matrix(unlist(g2), ncol = length(g2))) )
```

#### ...and so on for as many generations as necessary

## With replication

### To get our probabilities, we simply wrap it in `replicate()` and repeat the process 10,000x

#### The tricky part is getting the replication to work with however many generations are specified. We manage this by using a for loop
```{r, cache=TRUE}
  g <- list(data.frame(replicate(2, c(c(sample(c(20, 10), 1), sample(c(20, 10), 1)), c(sample(c(2, 1), 1), sample(c(2, 1), 1))))))


offsprings <- data.frame(replicate(10000, {

  for (i in 2:k) {

    g.tmp <- sapply(g[[i-1]], function(x) data.frame(replicate(2, c(c(sample(x[1:2], 1), sample(c(20, 10), 1)), c(sample(x[3:4], 1), sample(c(2, 1), 1))))))

  g[[i]] <- data.frame(matrix(unlist(g.tmp), ncol = length(g.tmp)))
  }

  sapply(g[[k]], sum)
  }))
```

## Calculating the probability

### We then count the occurrences where our summed values equal 33

#### This will only be '1, 2, 10, 20' geneotypes, and agnostic of order
```{r}
are.het <- data.frame(sapply(offsprings, function(x) x == 33))

kable(are.het[1:10])
```

### And check that there are at least N occurences of 33
```{r}
per.gen <- sapply(are.het, function(x) length(which(x == TRUE)) >= N)

per.gen[1:10]
```

### Finally calculate the probability
```{r}
sum(per.gen)/ ncol(are.het)
```

## CAVEAT

### My answers are **WRONG**
```{r}
pbinom(N-1, 2^k, 0.25, lower.tail=F)
```
